Resting energy expenditure of women with and without polycystic ovary syndrome: a systematic review and meta-analysis\thanks{Corresponding author: James Steele (Email: james@steele-research.com; ORCID: 0000-0002-8003-0757)}

### 2025-12-05 manuscript/submission_manuscript.tex
Add doi to preprint

The current study has multiple strengths stemming from its
preregistered, comprehensive methodology and Bayesian statistical
approach. This statistical framework allowed us to incorporate studies
with and without control groups to better estimate REE in women with and
without PCOS and to perform multiple sensitivity analyses that confirmed
the stability of our findings. However, a limitation here is that
variability in methods across studies, such as differences in PCOS
diagnostic criteria and REE testing protocols, may have influenced
results and the relatively small number of studies overall limits the
extent to which we can explore these potential moderators. Furthermore,
some studies controlled for body weight or body composition when
reporting REE values, while others did not. We accounted for this by
estimating or converting reported data to obtain unadjusted REE values
across all groups, thereby reducing this variability and further as
noted above provided estimates adjusted for BMI and fat-free mass both
of which had little influence on our conclusions. Another limitation is
that, due to fewer total control groups than PCOS groups, informed
priors were required in several statistical models. However, in the
context of Bayesian meta-analysis this can also be considered a
strength. Additionally, some studies reported data inconsistencies that
could not be clarified (e.g.,\textsuperscript{13,35--37}) and were
dropped from our main analysis though our conclusions again did not
qualitative change when we conducted sensitivity analyses including
these studies. Finally, most included studies were cross-sectional or
baseline assessments within intervention trials, which limits causal
inference. Indeed, we did not pre-register any kind of causal model
(e.g., a directed acyclic graph) to inform our analysis approach for
causal inference and as such have been explicit about the estimates
presented as being descriptive.

@@

\bibitem[\citeproctext]{ref-pagePRISMA2020Statement2021a}
\CSLLeftMargin{30. }%
\CSLRightInline{Page MJ, McKenzie JE, Bossuyt PM, et al. The {PRISMA}
2020 statement: An updated guideline for reporting systematic reviews.
\emph{BMJ}. 2021;372:n71.
doi:\href{https://doi.org/10.1136/bmj.n71}{10.1136/bmj.n71}}

\bibitem[\citeproctext]{ref-haddawayPRISMA2020PackageShiny2022}
\CSLLeftMargin{31. }%
\CSLRightInline{Haddaway NR, Page MJ, Pritchard CC, McGuinness LA.
{PRISMA2020}: {An R} package and {Shiny} app for producing {PRISMA}
2020-compliant flow diagrams, with interactivity for optimised digital
transparency and {Open Synthesis}. \emph{Campbell Systematic Reviews}.
2022;18(2):e1230.
doi:\href{https://doi.org/10.1002/cl2.1230}{10.1002/cl2.1230}}

\bibitem[\citeproctext]{ref-weberApplyingMetaAnalyticPredictivePriors2021}
\CSLLeftMargin{32. }%
\CSLRightInline{Weber S, Li Y, Iii JWS, Kakizume T, Schmidli H. Applying
{Meta-Analytic-Predictive Priors} with the {R Bayesian Evidence
Synthesis Tools}. \emph{Journal of Statistical Software}. 2021;100:1-32.
doi:\href{https://doi.org/10.18637/jss.v100.i19}{10.18637/jss.v100.i19}}

\bibitem[\citeproctext]{ref-wanEstimatingSampleMean2014}
\CSLLeftMargin{33. }%
\CSLRightInline{Wan X, Wang W, Liu J, Tong T. Estimating the sample mean
and standard deviation from the sample size, median, range and/or
interquartile range. \emph{BMC Medical Research Methodology}.
2014;14(1):135.
doi:\href{https://doi.org/10.1186/1471-2288-14-135}{10.1186/1471-2288-14-135}}

\bibitem[\citeproctext]{ref-pohlmeierEffectLowstarchLowdairy2014}
\CSLLeftMargin{34. }%
\CSLRightInline{Pohlmeier AM, Phy JL, Watkins P, et al. Effect of a
low-starch/low-dairy diet on fat oxidation in overweight and obese women
with polycystic ovary syndrome. \emph{Applied Physiology, Nutrition, and
Metabolism = Physiologie Appliquee, Nutrition Et Metabolisme}.
2014;39(11):1237-1244.
doi:\href{https://doi.org/10.1139/apnm-2014-0073}{10.1139/apnm-2014-0073}}

\bibitem[\citeproctext]{ref-kritikouA2BV3Adrenergic2006}
\CSLLeftMargin{35. }%
\CSLRightInline{Kritikou S, Saltamavros AD, Adonakis G, et al. The
{\(\alpha\)2B} and {\(\beta\)}3 adrenergic receptor genes polymorphisms
in women with polycystic ovarian syndrome ({PCOS}) and their association
with insulin resistance and basal metabolic rate ({BMR}). \emph{Review
of Clinical Pharmacology and Pharmacokinetics -- International Edition}.
2006;2006(2).}

\bibitem[\citeproctext]{ref-saltamavrosAlpha2Beta2007}
\CSLLeftMargin{36. }%
\CSLRightInline{Saltamavros AD, Adonakis G, Kritikou S, et al. Alpha 2
beta adrenoreceptor 301-303 deletion polymorphism in polycystic ovary
syndrome. \emph{Clinical Autonomic Research: Official Journal of the
Clinical Autonomic Research Society}. 2007;17(2):112-114.
doi:\href{https://doi.org/10.1007/s10286-007-0403-6}{10.1007/s10286-007-0403-6}}

\bibitem[\citeproctext]{ref-koikaAssociationPro12AlaPolymorphism2009}
\CSLLeftMargin{37. }%
\CSLRightInline{Koika V, Marioli DJ, Saltamavros AD, et al. Association
of the {Pro12Ala} polymorphism in peroxisome proliferator-activated
receptor Gamma2 with decreased basic metabolic rate in women with
polycystic ovary syndrome. \emph{European Journal of Endocrinology}.
2009;161(2):317-322.
doi:\href{https://doi.org/10.1530/EJE-08-1014}{10.1530/EJE-08-1014}}

\bibitem[\citeproctext]{ref-rodriguez-sanchezGratefulFacilitateCitation2023}
\CSLLeftMargin{38. }%
\CSLRightInline{Rodriguez-Sanchez F, cre, cph, Jackson CP, Hutchins SD,
Clawson JM. Grateful: {Facilitate Citation} of {R Packages}. Published
online October 2023.}

\bibitem[\citeproctext]{ref-cummingNewStatisticsWhy2014}
\CSLLeftMargin{39. }%
\CSLRightInline{Cumming G. The {New Statistics}: {Why} and {How}.
\emph{Psychological Science}. 2014;25(1):7-29.
doi:\href{https://doi.org/10.1177/0956797613504966}{10.1177/0956797613504966}}

\bibitem[\citeproctext]{ref-kruschkeBayesianNewStatistics2018}
\CSLLeftMargin{40. }%
\CSLRightInline{Kruschke JK, Liddell TM. The {Bayesian New Statistics}:
{Hypothesis} testing, estimation, meta-analysis, and power analysis from
a {Bayesian} perspective. \emph{Psychonomic Bulletin \& Review}.
2018;25:178-206.}

\bibitem[\citeproctext]{ref-usheyRenvProjectEnvironments2023}
\CSLLeftMargin{41. }%
\CSLRightInline{Ushey K, cre, Wickham H, Software P, PBC. Renv: {Project
Environments}. Published online September 2023.}

\bibitem[\citeproctext]{ref-landauTargetsDynamicFunctionOriented2023}
\CSLLeftMargin{42. }%
\CSLRightInline{Landau WM, Warkentin MT, Edmondson M, Oliver S, Mahr T,
Company EL and. Targets: {Dynamic Function-Oriented} '{Make}'-{Like
Declarative Pipelines}. Published online October 2023.}

\bibitem[\citeproctext]{ref-viechtbauerMetaforMetaAnalysisPackage2023}
\CSLLeftMargin{43. }%
\CSLRightInline{Viechtbauer W. Metafor: {Meta-Analysis Package} for {R}.
Published online September 2023.}

\bibitem[\citeproctext]{ref-burknerBrmsBayesianRegression2023}
\CSLLeftMargin{44. }%
\CSLRightInline{Bürkner PC, Gabry J, Weber S, et al. Brms: {Bayesian
Regression Models} using '{Stan}'. Published online September 2023.}

\bibitem[\citeproctext]{ref-arel-bundockMarginaleffectsPredictionsComparisons2023}
\CSLLeftMargin{45. }%
\CSLRightInline{Arel-Bundock V, cre, cph, Diniz MA, Greifer N, Bacher E.
Marginaleffects: {Predictions}, {Comparisons}, {Slopes}, {Marginal
Means}, and {Hypothesis Tests}. Published online October 2023.}

\bibitem[\citeproctext]{ref-kayTidybayesTidyData2023}
\CSLLeftMargin{46. }%
\CSLRightInline{Kay M, Mastny T. Tidybayes: {Tidy Data} and '{Geoms}'
for {Bayesian Models}. Published online August 2023.}

\bibitem[\citeproctext]{ref-wickhamGgplot2CreateElegant2023}
\CSLLeftMargin{47. }%
\CSLRightInline{Wickham H, Chang W, Henry L, et al. Ggplot2: {Create
Elegant Data Visualisations Using} the {Grammar} of {Graphics}.
Published online October 2023.}

\bibitem[\citeproctext]{ref-pedersenPatchworkComposerPlots2023}
\CSLLeftMargin{48. }%
\CSLRightInline{Pedersen TL. Patchwork: {The Composer} of {Plots}.
Published online August 2023.}

\bibitem[\citeproctext]{ref-hongBayesianMissingData2016}
\CSLLeftMargin{49. }%
\CSLRightInline{Hong H, Chu H, Zhang J, Carlin BP. A {Bayesian} missing
data framework for generalized multiple outcome mixed treatment
comparisons. \emph{Research Synthesis Methods}. 2016;7(1):6-22.
doi:\href{https://doi.org/10.1002/jrsm.1153}{10.1002/jrsm.1153}}

\bibitem[\citeproctext]{ref-velasquezUseAmmoniaInhalants2011}
\CSLLeftMargin{50. }%
\CSLRightInline{Velasquez JR. The {Use} of {Ammonia Inhalants Among
Athletes}. \emph{Strength \& Conditioning Journal}. 2011;33(2):33.
doi:\href{https://doi.org/10.1519/SSC.0b013e3181fd5c9b}{10.1519/SSC.0b013e3181fd5c9b}}

\bibitem[\citeproctext]{ref-pavlidouRevisedHarrisBenedict2023}
\CSLLeftMargin{51. }%
\CSLRightInline{Pavlidou E, Papadopoulou SK, Seroglou K, Giaginis C.
Revised {Harris}--{Benedict Equation}: {New Human Resting Metabolic Rate
Equation}. \emph{Metabolites}. 2023;13(2):189.
doi:\href{https://doi.org/10.3390/metabo13020189}{10.3390/metabo13020189}}

\bibitem[\citeproctext]{ref-steeleMetaanalysisVariationSport2023a}
\CSLLeftMargin{52. }%
\CSLRightInline{Steele J, Fisher, Smith, Schoenfeld, Yang, and Nakagawa
S. Meta-analysis of variation in sport and exercise science: {Examples}
of application within resistance training research. \emph{Journal of
Sports Sciences}. 2023;41(17):1617-1634.
doi:\href{https://doi.org/10.1080/02640414.2023.2286748}{10.1080/02640414.2023.2286748}}

\bibitem[\citeproctext]{ref-moranShorttermMealReplacements2006}
\CSLLeftMargin{53. }%
\CSLRightInline{Moran LJ, Noakes M, Clifton PM, Wittert GA, Williams G,
Norman RJ. Short-term meal replacements followed by dietary
macronutrient restriction enhance weight loss in polycystic ovary
syndrome. \emph{The American Journal of Clinical Nutrition}.
2006;84(1):77-87.
doi:\href{https://doi.org/10.1093/ajcn/84.1.77}{10.1093/ajcn/84.1.77}}

\bibitem[\citeproctext]{ref-brunerEffectsExerciseNutritional2006}
\CSLLeftMargin{54. }%
\CSLRightInline{Bruner B, Chad K, Chizen D. Effects of exercise and
nutritional counseling in women with polycystic ovary syndrome.
\emph{Applied Physiology, Nutrition, and Metabolism = Physiologie
Appliquee, Nutrition Et Metabolisme}. 2006;31(4):384-391.
doi:\href{https://doi.org/10.1139/h06-007}{10.1139/h06-007}}

\bibitem[\citeproctext]{ref-robinsonPostprandialThermogenesisReduced1992}
\CSLLeftMargin{55. }%
\CSLRightInline{Robinson S, Chan SP, Spacey S, Anyaoku V, Johnston DG,
Franks S. Postprandial thermogenesis is reduced in polycystic ovary
syndrome and is associated with increased insulin resistance.
\emph{Clinical Endocrinology}. 1992;36(6):537-543.
doi:\href{https://doi.org/10.1111/j.1365-2265.1992.tb02262.x}{10.1111/j.1365-2265.1992.tb02262.x}}

\bibitem[\citeproctext]{ref-cosarRestingMetabolicRate2008}
\CSLLeftMargin{56. }%
\CSLRightInline{Cosar E, Köken G, Sahin FK, et al. Resting metabolic
rate and exercise capacity in women with polycystic ovary syndrome.
\emph{International Journal of Gynaecology and Obstetrics: The Official
Organ of the International Federation of Gynaecology and Obstetrics}.
2008;101(1):31-34.
doi:\href{https://doi.org/10.1016/j.ijgo.2007.10.011}{10.1016/j.ijgo.2007.10.011}}

\bibitem[\citeproctext]{ref-graffDietaryGlycemicIndex2013}
\CSLLeftMargin{57. }%
\CSLRightInline{Graff SK, Mário FM, Alves BC, Spritzer PM. Dietary
glycemic index is associated with less favorable anthropometric and
metabolic profiles in polycystic ovary syndrome women with different
phenotypes. \emph{Fertility and Sterility}. 2013;100(4):1081-1088.
doi:\href{https://doi.org/10.1016/j.fertnstert.2013.06.005}{10.1016/j.fertnstert.2013.06.005}}

\bibitem[\citeproctext]{ref-dohRelationshipAdiposityInsulin2016}
\CSLLeftMargin{58. }%
\CSLRightInline{Doh E, Mbanya A, Kemfang-Ngowa JD, et al. The
{Relationship} between {Adiposity} and {Insulin Sensitivity} in {African
Women Living} with the {Polycystic Ovarian Syndrome}: {A Clamp Study}.
\emph{International Journal of Endocrinology}. 2016;2016:9201701.
doi:\href{https://doi.org/10.1155/2016/9201701}{10.1155/2016/9201701}}

\bibitem[\citeproctext]{ref-rodriguesLowValidityPredictive2018}
\CSLLeftMargin{59. }%
\CSLRightInline{Rodrigues AM dos S, Costa ABP, Campos DL, et al. Low
validity of predictive equations for calculating resting energy
expenditure in overweight and obese women with polycystic ovary
syndrome. \emph{Journal of Human Nutrition and Dietetics}.
2018;31(2):266-275.
doi:\href{https://doi.org/10.1111/jhn.12498}{10.1111/jhn.12498}}

\bibitem[\citeproctext]{ref-tosiInsulinMediatedSubstrateUse2021}
\CSLLeftMargin{60. }%
\CSLRightInline{Tosi F, Villani M, Migazzi M, et al. Insulin-{Mediated
Substrate Use} in {Women With Different Phenotypes} of {PCOS}: The
{Role} of {Androgens}. \emph{The Journal of Clinical Endocrinology and
Metabolism}. 2021;106(9):e3414-e3425.
doi:\href{https://doi.org/10.1210/clinem/dgab380}{10.1210/clinem/dgab380}}

\bibitem[\citeproctext]{ref-broskeyAssessingEnergyRequirements2017}
\CSLLeftMargin{61. }%
\CSLRightInline{Broskey NT, Klempel MC, Gilmore LA, et al. Assessing
{Energy Requirements} in {Women With Polycystic Ovary Syndrome}: {A
Comparison Against Doubly Labeled Water}. \emph{The Journal of Clinical
Endocrinology and Metabolism}. 2017;102(6):1951-1959.
doi:\href{https://doi.org/10.1210/jc.2017-00459}{10.1210/jc.2017-00459}}

\bibitem[\citeproctext]{ref-tosiRestingEnergyExpenditure2024}
\CSLLeftMargin{62. }%
\CSLRightInline{Tosi F, Rosmini F, Gremes V, et al. Resting energy
expenditure in women with polycystic ovary syndrome. \emph{Human
Reproduction (Oxford, England)}. 2024;39(8):1794-1803.
doi:\href{https://doi.org/10.1093/humrep/deae129}{10.1093/humrep/deae129}}

\bibitem[\citeproctext]{ref-sanchez-garridoMetabolicDysfunctionPolycystic2020}
\CSLLeftMargin{63. }%
\CSLRightInline{Sanchez-Garrido MA, Tena-Sempere M. Metabolic
dysfunction in polycystic ovary syndrome: {Pathogenic} role of androgen
excess and potential therapeutic strategies. \emph{Molecular
Metabolism}. 2020;35:100937.
doi:\href{https://doi.org/10.1016/j.molmet.2020.01.001}{10.1016/j.molmet.2020.01.001}}

\bibitem[\citeproctext]{ref-leeIncreasedRiskDisordered2017}
\CSLLeftMargin{64. }%
\CSLRightInline{Lee I, Cooney LG, Saini S, et al. Increased risk of
disordered eating in~polycystic ovary syndrome. \emph{Fertility and
Sterility}. 2017;107(3):796-802.
doi:\href{https://doi.org/10.1016/j.fertnstert.2016.12.014}{10.1016/j.fertnstert.2016.12.014}}

\bibitem[\citeproctext]{ref-bernadettPrevalenceEatingDisorders2016}
\CSLLeftMargin{65. }%
\CSLRightInline{Bernadett M, Szemán-N A.
\href{https://www.ncbi.nlm.nih.gov/pubmed/27244869}{{{[}Prevalence of
eating disorders among women with polycystic ovary syndrome{]}}}.
\emph{Psychiatria Hungarica: A Magyar Pszichiatriai Tarsasag Tudomanyos
Folyoirata}. 2016;31(2):136-145.}

>>>>

The current study has multiple strengths stemming from its
preregistered, comprehensive methodology and Bayesian statistical
approach. This statistical framework allowed us to incorporate studies
with and without control groups to better estimate REE in women with and
without PCOS and to perform multiple sensitivity analyses that confirmed
the stability of our findings. However, a limitation here is that
variability in methods across studies, such as differences in PCOS
diagnostic criteria and REE testing protocols, may have influenced
results and the relatively small number of studies overall limits the
extent to which we can explore these potential moderators. Furthermore,
some studies controlled for body weight or body composition when
reporting REE values, while others did not. We accounted for this by
estimating or converting reported data to obtain unadjusted REE values
across all groups, thereby reducing this variability and further as
noted above provided estimates adjusted for BMI and fat-free mass both
of which had little influence on our conclusions. Another limitation is
that, due to fewer total control groups than PCOS groups, informed
priors were required in several statistical models. However, in the
context of Bayesian meta-analysis this can also be considered a
strength. Additionally, some studies reported data inconsistencies that
could not be clarified (e.g.,\textsuperscript{13,36--38}) and were
dropped from our main analysis though our conclusions again did not
qualitative change when we conducted sensitivity analyses including
these studies. Finally, most included studies were cross-sectional or
baseline assessments within intervention trials, which limits causal
inference. Indeed, we did not pre-register any kind of causal model
(e.g., a directed acyclic graph) to inform our analysis approach for
causal inference and as such have been explicit about the estimates
presented as being descriptive.

@@

\bibitem[\citeproctext]{ref-nguoExploringPhysiologicalFactors2025}
\CSLLeftMargin{30. }%
\CSLRightInline{Nguo K, McGowan M, Cowan S, et al. Exploring the
physiological factors relating to energy balance in women with
polycystic ovary syndrome: A scoping review. \emph{Nutrition Reviews}.
2025;83(1):160-174.
doi:\href{https://doi.org/10.1093/nutrit/nuad169}{10.1093/nutrit/nuad169}}

\bibitem[\citeproctext]{ref-pagePRISMA2020Statement2021a}
\CSLLeftMargin{31. }%
\CSLRightInline{Page MJ, McKenzie JE, Bossuyt PM, et al. The {PRISMA}
2020 statement: An updated guideline for reporting systematic reviews.
\emph{BMJ}. 2021;372:n71.
doi:\href{https://doi.org/10.1136/bmj.n71}{10.1136/bmj.n71}}

\bibitem[\citeproctext]{ref-haddawayPRISMA2020PackageShiny2022}
\CSLLeftMargin{32. }%
\CSLRightInline{Haddaway NR, Page MJ, Pritchard CC, McGuinness LA.
{PRISMA2020}: {An R} package and {Shiny} app for producing {PRISMA}
2020-compliant flow diagrams, with interactivity for optimised digital
transparency and {Open Synthesis}. \emph{Campbell Systematic Reviews}.
2022;18(2):e1230.
doi:\href{https://doi.org/10.1002/cl2.1230}{10.1002/cl2.1230}}

\bibitem[\citeproctext]{ref-weberApplyingMetaAnalyticPredictivePriors2021}
\CSLLeftMargin{33. }%
\CSLRightInline{Weber S, Li Y, Iii JWS, Kakizume T, Schmidli H. Applying
{Meta-Analytic-Predictive Priors} with the {R Bayesian Evidence
Synthesis Tools}. \emph{Journal of Statistical Software}. 2021;100:1-32.
doi:\href{https://doi.org/10.18637/jss.v100.i19}{10.18637/jss.v100.i19}}

\bibitem[\citeproctext]{ref-wanEstimatingSampleMean2014}
\CSLLeftMargin{34. }%
\CSLRightInline{Wan X, Wang W, Liu J, Tong T. Estimating the sample mean
and standard deviation from the sample size, median, range and/or
interquartile range. \emph{BMC Medical Research Methodology}.
2014;14(1):135.
doi:\href{https://doi.org/10.1186/1471-2288-14-135}{10.1186/1471-2288-14-135}}

\bibitem[\citeproctext]{ref-pohlmeierEffectLowstarchLowdairy2014}
\CSLLeftMargin{35. }%
\CSLRightInline{Pohlmeier AM, Phy JL, Watkins P, et al. Effect of a
low-starch/low-dairy diet on fat oxidation in overweight and obese women
with polycystic ovary syndrome. \emph{Applied Physiology, Nutrition, and
Metabolism = Physiologie Appliquee, Nutrition Et Metabolisme}.
2014;39(11):1237-1244.
doi:\href{https://doi.org/10.1139/apnm-2014-0073}{10.1139/apnm-2014-0073}}

\bibitem[\citeproctext]{ref-kritikouA2BV3Adrenergic2006}
\CSLLeftMargin{36. }%
\CSLRightInline{Kritikou S, Saltamavros AD, Adonakis G, et al. The
{\(\alpha\)2B} and {\(\beta\)}3 adrenergic receptor genes polymorphisms
in women with polycystic ovarian syndrome ({PCOS}) and their association
with insulin resistance and basal metabolic rate ({BMR}). \emph{Review
of Clinical Pharmacology and Pharmacokinetics -- International Edition}.
2006;2006(2).}

\bibitem[\citeproctext]{ref-saltamavrosAlpha2Beta2007}
\CSLLeftMargin{37. }%
\CSLRightInline{Saltamavros AD, Adonakis G, Kritikou S, et al. Alpha 2
beta adrenoreceptor 301-303 deletion polymorphism in polycystic ovary
syndrome. \emph{Clinical Autonomic Research: Official Journal of the
Clinical Autonomic Research Society}. 2007;17(2):112-114.
doi:\href{https://doi.org/10.1007/s10286-007-0403-6}{10.1007/s10286-007-0403-6}}

\bibitem[\citeproctext]{ref-koikaAssociationPro12AlaPolymorphism2009}
\CSLLeftMargin{38. }%
\CSLRightInline{Koika V, Marioli DJ, Saltamavros AD, et al. Association
of the {Pro12Ala} polymorphism in peroxisome proliferator-activated
receptor Gamma2 with decreased basic metabolic rate in women with
polycystic ovary syndrome. \emph{European Journal of Endocrinology}.
2009;161(2):317-322.
doi:\href{https://doi.org/10.1530/EJE-08-1014}{10.1530/EJE-08-1014}}

\bibitem[\citeproctext]{ref-rodriguez-sanchezGratefulFacilitateCitation2023}
\CSLLeftMargin{39. }%
\CSLRightInline{Rodriguez-Sanchez F, cre, cph, Jackson CP, Hutchins SD,
Clawson JM. Grateful: {Facilitate Citation} of {R Packages}. Published
online October 2023.}

\bibitem[\citeproctext]{ref-cummingNewStatisticsWhy2014}
\CSLLeftMargin{40. }%
\CSLRightInline{Cumming G. The {New Statistics}: {Why} and {How}.
\emph{Psychological Science}. 2014;25(1):7-29.
doi:\href{https://doi.org/10.1177/0956797613504966}{10.1177/0956797613504966}}

\bibitem[\citeproctext]{ref-kruschkeBayesianNewStatistics2018}
\CSLLeftMargin{41. }%
\CSLRightInline{Kruschke JK, Liddell TM. The {Bayesian New Statistics}:
{Hypothesis} testing, estimation, meta-analysis, and power analysis from
a {Bayesian} perspective. \emph{Psychonomic Bulletin \& Review}.
2018;25:178-206.}

\bibitem[\citeproctext]{ref-usheyRenvProjectEnvironments2023}
\CSLLeftMargin{42. }%
\CSLRightInline{Ushey K, cre, Wickham H, Software P, PBC. Renv: {Project
Environments}. Published online September 2023.}

\bibitem[\citeproctext]{ref-landauTargetsDynamicFunctionOriented2023}
\CSLLeftMargin{43. }%
\CSLRightInline{Landau WM, Warkentin MT, Edmondson M, Oliver S, Mahr T,
Company EL and. Targets: {Dynamic Function-Oriented} '{Make}'-{Like
Declarative Pipelines}. Published online October 2023.}

\bibitem[\citeproctext]{ref-viechtbauerMetaforMetaAnalysisPackage2023}
\CSLLeftMargin{44. }%
\CSLRightInline{Viechtbauer W. Metafor: {Meta-Analysis Package} for {R}.
Published online September 2023.}

\bibitem[\citeproctext]{ref-burknerBrmsBayesianRegression2023}
\CSLLeftMargin{45. }%
\CSLRightInline{Bürkner PC, Gabry J, Weber S, et al. Brms: {Bayesian
Regression Models} using '{Stan}'. Published online September 2023.}

\bibitem[\citeproctext]{ref-arel-bundockMarginaleffectsPredictionsComparisons2023}
\CSLLeftMargin{46. }%
\CSLRightInline{Arel-Bundock V, cre, cph, Diniz MA, Greifer N, Bacher E.
Marginaleffects: {Predictions}, {Comparisons}, {Slopes}, {Marginal
Means}, and {Hypothesis Tests}. Published online October 2023.}

\bibitem[\citeproctext]{ref-kayTidybayesTidyData2023}
\CSLLeftMargin{47. }%
\CSLRightInline{Kay M, Mastny T. Tidybayes: {Tidy Data} and '{Geoms}'
for {Bayesian Models}. Published online August 2023.}

\bibitem[\citeproctext]{ref-wickhamGgplot2CreateElegant2023}
\CSLLeftMargin{48. }%
\CSLRightInline{Wickham H, Chang W, Henry L, et al. Ggplot2: {Create
Elegant Data Visualisations Using} the {Grammar} of {Graphics}.
Published online October 2023.}

\bibitem[\citeproctext]{ref-pedersenPatchworkComposerPlots2023}
\CSLLeftMargin{49. }%
\CSLRightInline{Pedersen TL. Patchwork: {The Composer} of {Plots}.
Published online August 2023.}

\bibitem[\citeproctext]{ref-hongBayesianMissingData2016}
\CSLLeftMargin{50. }%
\CSLRightInline{Hong H, Chu H, Zhang J, Carlin BP. A {Bayesian} missing
data framework for generalized multiple outcome mixed treatment
comparisons. \emph{Research Synthesis Methods}. 2016;7(1):6-22.
doi:\href{https://doi.org/10.1002/jrsm.1153}{10.1002/jrsm.1153}}

\bibitem[\citeproctext]{ref-velasquezUseAmmoniaInhalants2011}
\CSLLeftMargin{51. }%
\CSLRightInline{Velasquez JR. The {Use} of {Ammonia Inhalants Among
Athletes}. \emph{Strength \& Conditioning Journal}. 2011;33(2):33.
doi:\href{https://doi.org/10.1519/SSC.0b013e3181fd5c9b}{10.1519/SSC.0b013e3181fd5c9b}}

\bibitem[\citeproctext]{ref-pavlidouRevisedHarrisBenedict2023}
\CSLLeftMargin{52. }%
\CSLRightInline{Pavlidou E, Papadopoulou SK, Seroglou K, Giaginis C.
Revised {Harris}--{Benedict Equation}: {New Human Resting Metabolic Rate
Equation}. \emph{Metabolites}. 2023;13(2):189.
doi:\href{https://doi.org/10.3390/metabo13020189}{10.3390/metabo13020189}}

\bibitem[\citeproctext]{ref-steeleMetaanalysisVariationSport2023a}
\CSLLeftMargin{53. }%
\CSLRightInline{Steele J, Fisher, Smith, Schoenfeld, Yang, and Nakagawa
S. Meta-analysis of variation in sport and exercise science: {Examples}
of application within resistance training research. \emph{Journal of
Sports Sciences}. 2023;41(17):1617-1634.
doi:\href{https://doi.org/10.1080/02640414.2023.2286748}{10.1080/02640414.2023.2286748}}

\bibitem[\citeproctext]{ref-moranShorttermMealReplacements2006}
\CSLLeftMargin{54. }%
\CSLRightInline{Moran LJ, Noakes M, Clifton PM, Wittert GA, Williams G,
Norman RJ. Short-term meal replacements followed by dietary
macronutrient restriction enhance weight loss in polycystic ovary
syndrome. \emph{The American Journal of Clinical Nutrition}.
2006;84(1):77-87.
doi:\href{https://doi.org/10.1093/ajcn/84.1.77}{10.1093/ajcn/84.1.77}}

\bibitem[\citeproctext]{ref-brunerEffectsExerciseNutritional2006}
\CSLLeftMargin{55. }%
\CSLRightInline{Bruner B, Chad K, Chizen D. Effects of exercise and
nutritional counseling in women with polycystic ovary syndrome.
\emph{Applied Physiology, Nutrition, and Metabolism = Physiologie
Appliquee, Nutrition Et Metabolisme}. 2006;31(4):384-391.
doi:\href{https://doi.org/10.1139/h06-007}{10.1139/h06-007}}

\bibitem[\citeproctext]{ref-robinsonPostprandialThermogenesisReduced1992}
\CSLLeftMargin{56. }%
\CSLRightInline{Robinson S, Chan SP, Spacey S, Anyaoku V, Johnston DG,
Franks S. Postprandial thermogenesis is reduced in polycystic ovary
syndrome and is associated with increased insulin resistance.
\emph{Clinical Endocrinology}. 1992;36(6):537-543.
doi:\href{https://doi.org/10.1111/j.1365-2265.1992.tb02262.x}{10.1111/j.1365-2265.1992.tb02262.x}}

\bibitem[\citeproctext]{ref-cosarRestingMetabolicRate2008}
\CSLLeftMargin{57. }%
\CSLRightInline{Cosar E, Köken G, Sahin FK, et al. Resting metabolic
rate and exercise capacity in women with polycystic ovary syndrome.
\emph{International Journal of Gynaecology and Obstetrics: The Official
Organ of the International Federation of Gynaecology and Obstetrics}.
2008;101(1):31-34.
doi:\href{https://doi.org/10.1016/j.ijgo.2007.10.011}{10.1016/j.ijgo.2007.10.011}}

\bibitem[\citeproctext]{ref-graffDietaryGlycemicIndex2013}
\CSLLeftMargin{58. }%
\CSLRightInline{Graff SK, Mário FM, Alves BC, Spritzer PM. Dietary
glycemic index is associated with less favorable anthropometric and
metabolic profiles in polycystic ovary syndrome women with different
phenotypes. \emph{Fertility and Sterility}. 2013;100(4):1081-1088.
doi:\href{https://doi.org/10.1016/j.fertnstert.2013.06.005}{10.1016/j.fertnstert.2013.06.005}}

\bibitem[\citeproctext]{ref-dohRelationshipAdiposityInsulin2016}
\CSLLeftMargin{59. }%
\CSLRightInline{Doh E, Mbanya A, Kemfang-Ngowa JD, et al. The
{Relationship} between {Adiposity} and {Insulin Sensitivity} in {African
Women Living} with the {Polycystic Ovarian Syndrome}: {A Clamp Study}.
\emph{International Journal of Endocrinology}. 2016;2016:9201701.
doi:\href{https://doi.org/10.1155/2016/9201701}{10.1155/2016/9201701}}

\bibitem[\citeproctext]{ref-rodriguesLowValidityPredictive2018}
\CSLLeftMargin{60. }%
\CSLRightInline{Rodrigues AM dos S, Costa ABP, Campos DL, et al. Low
validity of predictive equations for calculating resting energy
expenditure in overweight and obese women with polycystic ovary
syndrome. \emph{Journal of Human Nutrition and Dietetics}.
2018;31(2):266-275.
doi:\href{https://doi.org/10.1111/jhn.12498}{10.1111/jhn.12498}}

\bibitem[\citeproctext]{ref-tosiInsulinMediatedSubstrateUse2021}
\CSLLeftMargin{61. }%
\CSLRightInline{Tosi F, Villani M, Migazzi M, et al. Insulin-{Mediated
Substrate Use} in {Women With Different Phenotypes} of {PCOS}: The
{Role} of {Androgens}. \emph{The Journal of Clinical Endocrinology and
Metabolism}. 2021;106(9):e3414-e3425.
doi:\href{https://doi.org/10.1210/clinem/dgab380}{10.1210/clinem/dgab380}}

\bibitem[\citeproctext]{ref-broskeyAssessingEnergyRequirements2017}
\CSLLeftMargin{62. }%
\CSLRightInline{Broskey NT, Klempel MC, Gilmore LA, et al. Assessing
{Energy Requirements} in {Women With Polycystic Ovary Syndrome}: {A
Comparison Against Doubly Labeled Water}. \emph{The Journal of Clinical
Endocrinology and Metabolism}. 2017;102(6):1951-1959.
doi:\href{https://doi.org/10.1210/jc.2017-00459}{10.1210/jc.2017-00459}}

\bibitem[\citeproctext]{ref-tosiRestingEnergyExpenditure2024}
\CSLLeftMargin{63. }%
\CSLRightInline{Tosi F, Rosmini F, Gremes V, et al. Resting energy
expenditure in women with polycystic ovary syndrome. \emph{Human
Reproduction (Oxford, England)}. 2024;39(8):1794-1803.
doi:\href{https://doi.org/10.1093/humrep/deae129}{10.1093/humrep/deae129}}

\bibitem[\citeproctext]{ref-sanchez-garridoMetabolicDysfunctionPolycystic2020}
\CSLLeftMargin{64. }%
\CSLRightInline{Sanchez-Garrido MA, Tena-Sempere M. Metabolic
dysfunction in polycystic ovary syndrome: {Pathogenic} role of androgen
excess and potential therapeutic strategies. \emph{Molecular
Metabolism}. 2020;35:100937.
doi:\href{https://doi.org/10.1016/j.molmet.2020.01.001}{10.1016/j.molmet.2020.01.001}}

\bibitem[\citeproctext]{ref-leeIncreasedRiskDisordered2017}
\CSLLeftMargin{65. }%
\CSLRightInline{Lee I, Cooney LG, Saini S, et al. Increased risk of
disordered eating in~polycystic ovary syndrome. \emph{Fertility and
Sterility}. 2017;107(3):796-802.
doi:\href{https://doi.org/10.1016/j.fertnstert.2016.12.014}{10.1016/j.fertnstert.2016.12.014}}
